---
title: 'Supplementar Material - Sexual and Gametogenesis on Sea Anemones: a Systematic Scope Review (Graph Codes)'
author: "Rafael Brandão"
date: "06/02/2023"
output:
  pdf_document:
    toc: yes
  word_document: 
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
font-size: 12
bibliography: bibliography.bib
editor_options:
  markdown:
    wrap: 72
---
\

### IMPORTANT: 

All images below (except for Figures 1, 7 and Supplementar Figure 1) were generated using gametrev2.csv spreadsheet.

Figure 1 was generate using model proposed by Tricco et al. 2018

Figures 7 and Supplementar Figure 1 were generated using table peak.csv, which was created from gametrev2.csv

\
\


\


## Libraries

```{r Library, include=TRUE, warning=FALSE, message=FALSE}
if (!require('paletteer'))      install.packages('paletteer');           library('paletteer')
if (!require('tidyverse'))  install.packages('tidyverse');       library('tidyverse')
if (!require('ggplot2'))       install.packages('ggplot2');            library('ggplot2')
if (!require('ggpubr'))       install.packages('ggpubr');            library('ggpubr')

setwd('C:/Users/rabra/OneDrive/Área de Trabalho/Bibliometria/Reprodução/Graficos/Gamtoreview')

gameterev<-read.csv2("gametrev2.csv")

```

\

## Number of studies throught the years 
\
\

```{r, fig.height=5, fig.width=12,echo=TRUE,message=FALSE, warning=FALSE}
#tiff(file="Images/Temporal distribution of studies.tiff",width=10, height=8, units="in", res=300)
gameterev%>%
  transform(year=as.numeric(year))%>%
  ggplot(aes(year)) + 
           geom_bar(color="darkgray", 
                    fill= "darkgray", 
                    alpha=0.7) +
           theme_classic(base_size = 20) +
  theme(axis.text.x = element_text(size = 20),axis.text.y=element_text(size = 20),
        axis.line.y = element_blank())+
  scale_x_continuous(n.breaks=15)+
  scale_y_continuous(n.breaks=4) +
  labs(y="Number of studies", x= "Year")

#dev.off()


```
\


## Number of studies per family 
\
\

```{r, fig.height=10, fig.width=12,echo=TRUE, message=FALSE, warning=FALSE}
#tiff(file="Images/Number_species_studied_family_depth.tiff",width=20, height=16, units="in", res=300)

histfamily<-read.csv2("gametrev2.csv")%>%
select(family,species, depth)%>%
unite("specifam", family:species, remove=FALSE)%>%
unique() 
ggplot(histfamily) + 
  geom_bar(aes( fill=depth, family)) + 
  theme_classic(base_size = 40) + labs(y="Number of species", x ="Family") +
  #theme(axis.text.x = element_text(size = 30),axis.text.y=element_text(size = 30)) +
  scale_x_discrete(limits=c("Incertae sedis", "Kadosactinidae", "Capneidae", 
                            "Actinostolidae","Diadumenidae",
                            "Edwardsiidae","Metridiidae","Amphianthidae","Gonactiniidae", "Phymanthidae", 
                            "Sagartiidae","Aiptasiidae","Hormathiidae", "Actiniidae")) +
  scale_fill_manual(values=c('navy', 'darkgray'))+
  labs(y="Number of species", x ="Family", fill= 'Depth') +
  coord_flip() +
  theme(legend.position = "bottom", axis.line.y = element_blank()) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA), n.breaks = 25)
#dev.off()
```

\

## Number of studies for Actiniidae species  
\
\

```{r,echo=TRUE, message=FALSE, warning=FALSE}
tiff(file="Images/Number_spcies_actiniidae.tiff",width=20, height=16, units="in", res=300)

histspecie<-read.csv2("gametrev2.csv")%>%
select(family,species)%>%
filter(family=="Actiniidae")%>%
drop_na()
ggplot(histspecie) + 
  geom_bar(aes(species),fill= 'darkgray', alpha = 0.8) + 
  theme_classic(base_size = 40) + 
  scale_y_continuous(n.breaks = 5, expand = c(0, 0), limits = c(0, NA)) +
  scale_x_discrete(limits=c('Urticina lofotensis', 'Anthopleura xanthogrammica', 'Anthopleura handi', 'Anthopleura dixoniana', 'Anthopleura asiatica', 'Anemonia viridis', 'Actinia bermudensis','Epiactis prolifera','Anemonia sulcata', 'Condylactis gigantea', 'Entacmaea quadricolor', 'Anthopleura elegantissima', 'Actinia tenebrosa', 'Bunodosoma cavernata', 'Actinia fragacea', 'Actinia equina')) +
  scale_fill_manual(values=c( 'darkgray','navy', 'lightgray')) +
  labs(y="Number of times studied", x ="Species", fill= element_blank()) +
  coord_flip() + 
  theme(legend.position = "bottom", axis.line.y = element_blank())

dev.off()
```

## Presence of hermaphrodites per family using all species registers 

```{r, fig.width=18, fig.hight=25 ,echo=TRUE, message=FALSE, warning=FALSE}
#tiff(file="Images/Hermaphrodites.tiff",width=20, height=16, units="in", res=300)

gameterev%>%
  group_by(hermaphro, species)%>%
  ggplot() + geom_bar(aes(family, fill=hermaphro)) +  
  theme_classic(base_size = 30) + labs(x= 'Family', y= "Registers") + 
  #theme(axis.text.x = element_text(size=30),axis.text.y=element_text(size = 30)) +
  scale_x_discrete(limits=c("Incertae sedis", "Kadosactinidae", "Capneidae", 
                             "Actinostolidae","Amphianthidae","Diadumenidae",
                            "Phymanthidae","Edwardsiidae","Metridiidae",
                            "Gonactiniidae", "Hormathiidae","Sagartiidae",
                            "Aiptasiidae", "Actiniidae")) +
  labs(fill="Presence of Hermaphordites")+
  scale_fill_manual(values=c('darkgray', 'darkgreen')) +
  coord_flip() +
  scale_y_continuous(n.breaks = 20, expand = c(0, 0), limits = c(0, NA)) +
  theme(legend.position = "bottom", axis.line.y = element_blank())

#dev.off()
```
## Figure 6 is a map done outside R


##  Reproductive peak by realm 
\
\


```{r, echo=TRUE}
especies <- c( 'Entacmaea quadricolor', 'Actinoporus elongatus','Anthothoe albocincta',  'Actinia tenebrosa', 'Anthopleura handi','Phymanthus strandesi','Anthopleura dixoniana','Exaiptasia pallida', 'Diadumene lineata','Anthopleura elegantissima', 'Anthopleura xanthogrammica', 'Epiactis lisbethae', 'Cribrinopsis fernaldi', 'Aulactinia sinensis', 'Anthopleura asiatica', 'Epiactis prolifera', 'Actinia equina','Metridium senile','Protanthea simplex', 'Gonactinia  prolifera','Cereus pedunculatus','Anemonia viridis', 'Exaiptasia diaphana', 'Cylista troglodites','Anemonia sulcata', 'Cylista elegans', 'Actinia fragacea', 'Allantactis parasitica', 'Phelliactis hertwig', 'Phelliactis robusta','Amphianthus dorhni', 'Paracalliactis stephensoni', 'Actinia bermudensis','Condylactis gigantea', 'Bartholomea annulata', 'Phymanthus crucifer',  'Bunodosoma cavernata' )

colors <- c('#e76f51','#287271','#ffd166','#06d6a0','#118ab2','#f4a261','#073b4c')

colors2 <- c('#e76f51','#287271','#ffd166','#06d6a0','#118ab2','#f4a261','#7f5539',
             '#073b4c', '#93b7be')

```

```{r, message=FALSE,echo=TRUE, warning=FALSE, include=TRUE, paged.print=FALSE}
gamepeak<-read.csv2("peak.csv")%>%
rename(realm = 1)
gamepeakmale<- select(gamepeak,1,2,3,4,6)%>%
separate_rows(malepeak, sep="/")%>%
group_by(realm)%>%
drop_na()

e<-ggplot(gamepeakmale) + 
  annotate(geom = "rect", ymin = 4.5, ymax = Inf,
           xmin = -Inf, xmax =3.6, alpha=0.15, fill="gray") + 
  annotate(geom = "rect", ymin = 4.5, ymax = Inf,
           xmin = 12.6, xmax =13, alpha=0.15, fill="gray") +
  annotate(geom = "rect", ymin = 4.5, ymax = Inf,
           xmin = 6.6, xmax =9.6, alpha=0.35, fill="gray") + 
  annotate(geom = "rect", ymin = -Inf, ymax = 4.5,
           xmin = -Inf, xmax =3.6, alpha=0.35, fill="gray") + 
  annotate(geom = "rect", ymin = -Inf, ymax = 4.5,
           xmin = 12.6, xmax =13, alpha=0.35, fill="gray") +
  annotate(geom = "rect", ymin = -Inf, ymax = 4.5,
           xmin = 6.6, xmax =9.6, alpha=0.15, fill="gray") +
  geom_point(aes(malepeak, species, color= realm), 
             size= 75, shape=95, position= position_nudge(x=0.5)) +
  scale_x_discrete(limits=c("January", "February", "March", 
                            "April", "May", "June", 
                            "July", "August", "September", 
                            "October","November","December"), 
                   labels=c("Jan", "Feb", "Mar", 
                            "Apr", "May", "Jun", 
                            "Jul", "Aug", "Sep", 
                            "Oct", "Nov", "Dec")) + 
  scale_y_discrete(limits= especies, position = "right") +
  theme_classic(base_size = 36) + 
  labs(x="Months") +
  coord_cartesian(xlim= c(1.5,12.5), clip = "off") +
  labs(y=element_blank(), color="Marine Realm") + 
 theme(axis.text.y=element_text(face="italic", size =45), legend.position="bottom",
       axis.line.y = element_blank())+
   guides(color = guide_legend(override.aes = list(size = 20, shape= "square"), 
                               ncol = 1))+
  color_palette(palette = colors)




```
\

```{r, fig.height=12, fig.width=16, echo=TRUE, message=FALSE, warning=FALSE, include= TRUE}


gamepeak<-read.csv2("peak.csv")%>%
rename(realm = 1)
gamepeakfeme<- select(gamepeak,1,2,3,4,5)%>%
separate_rows(femepeak, sep="/")%>%
group_by(realm)%>%
drop_na()

t<-ggplot(gamepeakfeme) +
  annotate(geom = "rect", ymin = 4.5, ymax = Inf,
           xmin = -Inf, xmax =3.6, alpha=0.15, fill="gray") + 
  annotate(geom = "rect", ymin = 4.5, ymax = Inf, 
           xmin = 12.6, xmax =Inf, alpha=0.15, fill="gray") +
  annotate(geom = "rect", ymin = 4.5, ymax = Inf, 
           xmin = 6.6, xmax =9.6, alpha=0.35, fill="gray") + 
  annotate(geom = "rect", ymin = -Inf, ymax = 4.5, xmin = 1, 
           xmax =3.6, alpha=0.35, fill="gray") + 
  annotate(geom = "rect", ymin = -Inf, ymax = 4.5, xmin = 12.6, 
           xmax =Inf, alpha=0.35, fill="gray") +
  annotate(geom = "rect", ymin = -Inf, ymax = 4.5, xmin = 6.6, 
           xmax =9.6, alpha=0.15, fill="gray") +
  geom_point(aes(femepeak,species,color = realm), size= 75, shape=95, position= position_nudge(x=0.5)) + 
   scale_x_discrete(limits=c("January", "February", "March", 
                            "April", "May", "June", 
                            "July", "August", "September", 
                            "October","November","December"), 
                   labels=c("Jan", "Feb", "Mar", 
                            "Apr", "May", "Jun", 
                            "Jul", "Aug", "Sep", 
                            "Oct", "Nov", "Dec")) +
  theme_classic(base_size = 36) + 
  guides(color = guide_legend(override.aes = list(size = 20, shape= "square"),
                              ncol = 1))  +
  labs(x="Months") + 
  coord_cartesian(xlim= c(1.5,12.5), clip = "off")+
  labs(y=element_blank(),color="Marine Realm") + 
  scale_y_discrete(limits= especies) + 
  theme(axis.text.y=element_text(face="italic", size = 45), legend.position = "bottom",
        axis.line.y = element_blank())+
  color_palette(palette = colors) 
 

```


```{r,fig.height=25, fig.width=32, message=FALSE,echo=TRUE, warning=FALSE}
tiff(file="Images/Peak_reproduction.tiff",width=54, height=32, units="in", res=300)


ggarrange(t,e, common.legend = T)

dev.off()
```
\
\

## Evironmental factors influencing reproduction 
\
\
```{r, fig.height=10, fig.width=30,echo=TRUE, message=FALSE, warning=FALSE}
tiff(file="Images/Environmental_factors.tiff",width=32, height=10, units="in", res=300)
gameterev%>%
  select(environment_influence)%>%
  drop_na()%>%
  ggplot() + geom_bar(aes(environment_influence), 
                      fill='darkgray',width = 0.7, size=10) +
  theme_classic(base_size = 50) + 
  labs(x = 'Enviromental factors',y= "Number of studies") + 
  scale_shape_discrete (solid = F) +
  theme(axis.text.x = element_text(size = 50),
        axis.text.y=element_text(size = 50), axis.line.y = element_blank())+
  scale_y_continuous(n.breaks = 11, expand = c(0, 0), limits = c(0, NA)) +
  coord_flip() 
dev.off()
```
\
\

## Oocyte size per species using data from histological slide measurement only
\
\

```{r, fig.height=12, fig.width=23,echo=TRUE, message=FALSE, warning=FALSE}
#tiff(file="Images/Oocyte_size.tiff",width=30, height=18, units="in", res=300)
f<-gameterev%>%
  select(fixation, largoocy, species, family, province, realm)%>%
  filter(fixation=="slide")%>%
  drop_na()%>%
  ggplot() + geom_point(aes(largoocy, species, pch= family),
                        stroke=3.5, size=13) +  
  theme_classic(base_size = 35) + 
  labs(x= "Oocyte size (um)", y=element_blank()) +
  scale_x_continuous(n.breaks = 26)+ 
  scale_shape_manual (values = c(2,3,4,5,6,7,8,9,10)) +
  theme(axis.text.x = element_text(angle = 0, vjust =0, hjust=0.4, size = 30),
                          axis.text.y=element_text(face="italic", size = 40),
        expand = c(0, 0), limits = c(0, NA), legend.key.size = unit(2, 'cm'))+
  labs(color="Realm", shape="Family") +
  color_palette(palette = colors2) 
#dev.off()

```
\
\
```{r, fig.height=12, fig.width=23,echo=TRUE, message=FALSE, warning=FALSE}
#tiff(file="Images/Oocyte_size.tiff",width=30, height=18, units="in", res=300)
m<-gameterev%>%
  select(fixation, largoocy, species, family, province, realm)%>%
  filter(fixation=="slide")%>%
  drop_na()%>%
  ggplot() + geom_point(aes(largoocy, species,color=realm),
                        stroke=3.5, size=13) +  
  theme_classic(base_size = 35) + 
  labs(x= "Oocyte size (um)", y=element_blank()) +
  scale_x_continuous(n.breaks = 26)+
  theme(axis.text.x = element_text(angle = 0, vjust =0, hjust=0.4, size = 30),
                          axis.text.y=element_text(face="italic", size = 40),
        expand = c(0, 0), limits = c(0, NA), legend.key.size = unit(2, 'cm'),
        legend.position = 'left')+
  scale_y_discrete(position = "right") +
  labs(color="Realm", shape="Family") +
  color_palette(palette = colors2) 
#dev.off()

```


```{r,fig.height=25, fig.width=62, message=FALSE,echo=TRUE, warning=FALSE}
tiff(file="Images/Oocyte size.tiff",width=54, height=20, units="in", res=300)


ggarrange(f,m)

dev.off()
```




